Verifying Demonstrations

### 2018-02-26 paper/ZKPK.tex
Breaks up long equation
Breaks out ZKPK

\subsection{Zero-knowledge proofs of knowledge}%
\label{ZKPK}

Briefly describe zero-knowledge proofs and what type of properties can be proved 
using them, e.g.\ algebraic structures but not one-way functions.

@@

\subsection{Instantiations}

@@

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{equation*}
  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
  \land \PK{\beta}{B = g^\beta},
\end{equation*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \toprule

@@

    \bottomrule
  \end{tabular}
  \caption{%
    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

>>>>

\subsubsection{Zero-knowledge proofs of knowledge}%
\label{ZKPK}

@@

\subsubsection{Instantiations of the \acs{ZKPK} protocols}

@@

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \\
  \PK{\alpha}{A = g^\alpha} \land \PK{\beta}{B = g^\beta},
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

@@

  \end{tabular}
  \caption{%
    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}
